---
title: "Welcome to My Collection of Learning Materials"
description: |
  This site is where I will be storing my collected learning materials for using R for statistical data analysis, as well as for creating publication-worthy visualizations.
author:
  - name: Elizabeth Oneita Davis
date: 08-21-2019
preview: none
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(emo)
```

## Who am I?

I'm **Elizabeth Oneita Davis**, a postdoctoral associate in [Community Engagement](https://institute.sandiegozoo.org/community-engagement) at the [San Diego Zoo Institute for Conservation Research](https://institute.sandiegozoo.org/). I work on illegal wildlife trade in Cambodia, Laos, and Vietnam. In the course of my role, I also teach statistics and data analysis, using **R**. My intention is for this website to serve as a repository of information for any past, present, or future students I may have.

I also hope to eventually translate these materials into Vietnamese, so if you are a Vietnamese #rstats user who wants to collaborate in creating Vietnamese-language materials, please get in touch! 


```{r, child="../../data/rmds/favicons-elizabeth-davis.Rmd"}
```
```{r, child="../../data/rmds/acknowledgment_profile_hank.Rmd"}
```


